---
title: "Running simulations of MultipleContactNeutralMigrat.nlogo"
author: "Leonardo A. Saravia"
date: "8/11/2022"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE,echo=FALSE}
knitr::opts_chunk$set(echo = FALSE)

needed_packages <- c(
    "tidyverse"
  , "lubridate"
  , "future"
  , "tictoc"
  , "nlrx")

lapply(needed_packages, function(x) { if(!require(x,character.only = TRUE)) install.packages(x)} )

theme_set(theme_bw())
source("R/functions.r")

#
# Where the NetLogo model is
# Setup for nlrx 
#
if( Sys.info()['nodename'] =="ls-pro") {
  simfolder <- "/home/leonardo/Dropbox/Projects/DynamicForestExtinction"
  
} else if(Sys.info()['nodename'] =="biologia2018") {                     # Server UNGS
  simfolder <- "/home/leonardo/Dropbox/Projects/DynamicForestExtinction"                       

}

# Unix default NetLogo installation path (adjust to your needs!):
#
netlogopath <- file.path("/home/leonardo/NetLogo")
modelpath <- file.path(simfolder, "MultipleContactNeutralMigrat.nlogo")
outpath <- file.path(simfolder,"Simulations")

# If not defined set the JAVA version of your local 
if(Sys.getenv("JAVA_HOME")==""){
  Sys.setenv(JAVA_HOME = "/usr/lib/jvm/java-11-openjdk-amd64")
  ## "/usr/lib/jvm/java-8-oracle"
}

nl <- nl(nlversion = "6.2",
         nlpath = netlogopath,
         modelpath = modelpath,
         jvmmem = 2048)


```

## Why do several small patches hold more species that few large patches?

## Lambda = 4

* Initial conditions: migration from the regional community and after the area is filled of individuals, then 60% of the area degraded with regular patches (t= 200 for lambda=4 )

```{r SLOSS_lambda4_simulations_lambda4,echo=FALSE,message=FALSE,warning=FALSE,fig.align='center',eval=TRUE}

# pf = probability of fragmentation, hps = habitat patch size , dd=dispersal distance 
#
nl@experiment <- experiment(expname="NoSelection_pf06_hps3-61_dd1-3",
                            outpath=outpath,
                            repetition=1,
                            tickmetrics="false",
                            idsetup="setup",
                            idgo="go",
                            runtime=0,
                            metrics=c("birds-at-deforestation", "calc-number-of-species","calc-shannon-diversity","count birds", "mean-free-path"),
                            variables = list("birds-dispersal-distance" = list(values=c(1.1, 1.2, 1.5, 2, 3)),
                                              "habitat-patch-size" = list(values=c(3, 9, 29, 61))
                                             ),
                            constants = list("world-width" = 199,
                                             "world-height" = 199,
                                             "initial-population" = 0,
                                             "max-birds-species" = 100,
                                             "birth-rate-birds" = 4,
                                             "death-rate-birds" = 1,
                                             "migration-rate-birds" = 0.001,
                                             "Video" = "false",
                                             "prob-frag" =  0.6,
                                             "Deforestation-at-time" = 200,
                                             "end-time" = 1500,
                                             "Migration0-at-deforestation" = "false",
                                             "deforestation-type" = "\"regular\"",
                                             "birds-behavior" = "\"NoSelection\"",
                                             "replacement-rate" = 0.0
                                             ))


#
# Run 10 times this do not set the run variable for output 
#
# nseeds * number_of_parameters / split = 10 * 300 / 4 - total number of jobs = nseeds * split = 10*4
#

nl@simdesign <- simdesign_ff(nl=nl,
                               nseeds=10)

# run in Paralell 
#
plan(multisession)
tic()
results <- run_nl_all(nl,split = 4)
#results <- run_nl_all(nl,split = 4)
toc()
plan(sequential)
names(results)

#
# Write the output 
#
setsim(nl, "simoutput") <- results 
write_simoutput(nl)
```



```{r readSimulations, echo=FALSE,message=FALSE,warning=FALSE,fig.align='center',eval=FALSE}
# Read previous simulations
#
if( file.exists("Simulations/sloss_sim_ff.rds")) {

  sloss_sim <- readRDS("Simulations/sloss_sim_ff.rds") 
  
} else {
  sloss_sim <- tibble()
}

# Read netlogo simulations and 
# Convert the list of mean_free_path to degraded_mfp and non_degraded_mfp
#
mdl <- read_netlogo_simul(file.path(outpath,"NoSelection_pf06_hps3-61_dd1-3_ff.csv"),skip=0) %>% 
  mutate(mean_free_path=str_sub(mean_free_path,2,-2)) %>% 
  separate(mean_free_path, c("non_degraded_mfp","degraded_mfp"), sep=" ",convert=TRUE)


sloss_sim <- bind_rows(sloss_sim,mdl)


## Old code to plot 

# Neutral communities 
#
names(mdl)
#
# Plot for neutral communities 
#
mdl1 <- mdl %>% group_by(birds_dispersal_distance, habitat_patch_size) %>% summarise(across(birds_at_deforestation:count_birds,mean)) %>% mutate(deltaPop = (count_birds - birds_at_deforestation )/ birds_at_deforestation  )


# require(plotly)
# plot_ly(data=mdl1, x=~birds_dispersal_distance, y=~habitat_patch_size, z=~calc_number_of_species, type="scatter3d", mode="markers", color=~calc_number_of_species, marker = list(size = 1))

mdl1 %>% ggplot(aes(x=birds_dispersal_distance,y=calc_number_of_species,color=habitat_patch_size)) + geom_point() + scale_color_viridis_c(guide = FALSE) + facet_wrap( ~habitat_patch_size ) + theme_bw()

mdl1 %>% ggplot(aes(x=birds_dispersal_distance,y=calc_shannon_diversity,color=habitat_patch_size)) + geom_point() + scale_color_viridis_c(guide = FALSE) + facet_wrap( ~habitat_patch_size ) + theme_bw()

mdl1 %>% ggplot(aes(x=birds_dispersal_distance,y=deltaPop,color=habitat_patch_size)) + geom_point() + scale_color_viridis_c(guide = FALSE) + facet_wrap( ~habitat_patch_size ) + theme_bw()


mdl1 %>% filter(birds_dispersal_distance == 1.1 || birds_dispersal_distance == 3) %>% mutate(birds_dispersal_distance=factor(birds_dispersal_distance)) %>% ggplot(aes(x=habitat_patch_size,y=calc_number_of_species,color=birds_dispersal_distance)) + geom_point() + scale_color_viridis_d() + theme_bw()

# Plot for hierarchical communities 
#
mdl <- read_netlogo_simul("Simulations/MultipleContactNeutralMigrat_Hierarchical_pf06_hpf3-59_dd1-3.csv")
sloss_sim <- bind_rows(sloss_sim,mdl)

#
#
mdl1 <- mdl %>% group_by(birds_dispersal_distance, habitat_patch_size) %>% summarise(across(birds_at_deforestation:count_birds,mean)) %>% mutate(deltaPop = (count_birds - birds_at_deforestation )/ birds_at_deforestation  )

mdl1 %>% ggplot(aes(x=birds_dispersal_distance,y=calc_number_of_species,color=habitat_patch_size)) + geom_point() + scale_color_viridis_c(guide = FALSE) + facet_wrap( ~habitat_patch_size ) + theme_bw()

mdl1 %>% ggplot(aes(x=birds_dispersal_distance,y=calc_shannon_diversity,color=habitat_patch_size)) + geom_point() + scale_color_viridis_c(guide = FALSE) + facet_wrap( ~habitat_patch_size ) + theme_bw()

mdl1 %>% ggplot(aes(x=birds_dispersal_distance,y=deltaPop,color=habitat_patch_size)) + geom_point() + scale_color_viridis_c(guide = FALSE) + facet_wrap( ~habitat_patch_size ) + theme_bw()

mdl1 %>% filter(birds_dispersal_distance == 1.1 || birds_dispersal_distance == 3) %>% mutate(birds_dispersal_distance=factor(birds_dispersal_distance)) %>% ggplot(aes(x=habitat_patch_size,y=calc_number_of_species,color=birds_dispersal_distance)) + geom_point() + scale_color_viridis_d() + theme_bw()

# Plot for BirthSelection communities 
#
mdl <- read_netlogo_simul("Simulations/MultipleContactNeutralMigrat_BirthSelection_pf06_hpf3-59_dd1-3.csv")
sloss_sim <- bind_rows(sloss_sim,mdl)


#
#
mdl1 <- mdl %>% group_by(birds_dispersal_distance, habitat_patch_size) %>% summarise(across(birds_at_deforestation:count_birds,mean)) %>% mutate(deltaPop = (count_birds - birds_at_deforestation )/ birds_at_deforestation  )

mdl1 %>% ggplot(aes(x=birds_dispersal_distance,y=calc_number_of_species,color=habitat_patch_size)) + geom_point() + scale_color_viridis_c(guide = FALSE) + facet_wrap( ~habitat_patch_size ) + theme_bw()

mdl1 %>% ggplot(aes(x=birds_dispersal_distance,y=calc_shannon_diversity,color=habitat_patch_size)) + geom_point() + scale_color_viridis_c(guide = FALSE) + facet_wrap( ~habitat_patch_size ) + theme_bw()

mdl1 %>% ggplot(aes(x=birds_dispersal_distance,y=deltaPop,color=habitat_patch_size)) + geom_point() + scale_color_viridis_c(guide = FALSE) + facet_wrap( ~habitat_patch_size ) + theme_bw()

mdl1 %>% filter(birds_dispersal_distance == 1.1 || birds_dispersal_distance == 3) %>% mutate(birds_dispersal_distance=factor(birds_dispersal_distance)) %>% ggplot(aes(x=habitat_patch_size,y=calc_number_of_species,color=birds_dispersal_distance)) + geom_point() + scale_color_viridis_d() + theme_bw()

# check how many simulations 
mdl1 <-sloss_sim %>% count(habitat_patch_size,birds_dispersal_distance,birds_behavior)

```


## Lambda = 2

* For patch sizes 3 9 without connectivity between patches (dispersal 1.1 - 1.2 ) the patch populations get extinct 
* Here I added another field "Migration0_at_deforestation" 

```{r SLOSS_lambda4_simulations_lambda2,echo=FALSE,message=FALSE,warning=FALSE,fig.align='center',eval=FALSE}
require(tidyverse)

source("R/functions.r")

# Neutral communities 
#
# No migration after deforestation
mdl <- read_netlogo_simul("Simulations/NoSelection_pf06_hpf3-59_dd1-3_lambda2.csv")
sloss_sim <- bind_rows(sloss_sim,mdl)

## With migration
#
mdl <- read_netlogo_simul("Simulations/MultipleContactNeutralMigrat_NoSelection_pf06_hpf3-59_dd1-3_lambda2.csv")
sloss_sim <- bind_rows(sloss_sim,mdl)

names(mdl)
#
# Plot for neutral communities 
#
mdl1 <- mdl %>% group_by(birds_dispersal_distance, habitat_patch_size) %>% summarise(across(birds_at_deforestation:count_birds,mean)) %>% mutate(deltaPop = (count_birds - birds_at_deforestation )/ birds_at_deforestation  )


mdl1 %>% ggplot(aes(x=birds_dispersal_distance,y=calc_number_of_species,color=habitat_patch_size)) + geom_point() + scale_color_viridis_c(guide = FALSE) + facet_wrap( ~habitat_patch_size ) + theme_bw()

mdl1 %>% ggplot(aes(x=birds_dispersal_distance,y=calc_shannon_diversity,color=habitat_patch_size)) + geom_point() + scale_color_viridis_c(guide = FALSE) + facet_wrap( ~habitat_patch_size ) + theme_bw()

mdl1 %>% ggplot(aes(x=birds_dispersal_distance,y=deltaPop,color=habitat_patch_size)) + geom_point() + scale_color_viridis_c(guide = FALSE) + facet_wrap( ~habitat_patch_size ) + theme_bw()

mdl1 %>% filter(birds_dispersal_distance == 1.1 || birds_dispersal_distance == 3) %>% mutate(birds_dispersal_distance=factor(birds_dispersal_distance)) %>% ggplot(aes(x=habitat_patch_size,y=calc_number_of_species,color=birds_dispersal_distance)) + geom_point() + scale_color_viridis_d() + theme_bw()

# Plot for hierarchical communities 
#
mdl <- read_netlogo_simul("Simulations/Hierarchical_pf06_hpf3-59_dd1-3_lambda2.csv")
sloss_sim <- bind_rows(sloss_sim,mdl)

mdl <- read_netlogo_simul("Simulations/MultipleContactNeutralMigrat_Hierarchical_pf06_hpf3-59_dd1-3_lambda2.csv")
sloss_sim <- bind_rows(sloss_sim,mdl)


#
#
mdl1 <- mdl %>% group_by(birds_dispersal_distance, habitat_patch_size) %>% summarise(across(birds_at_deforestation:count_birds,mean)) %>% mutate(deltaPop = (count_birds - birds_at_deforestation )/ birds_at_deforestation  )

mdl1 %>% ggplot(aes(x=birds_dispersal_distance,y=calc_number_of_species,color=habitat_patch_size)) + geom_point() + scale_color_viridis_c(guide = FALSE) + facet_wrap( ~habitat_patch_size ) + theme_bw()

mdl1 %>% ggplot(aes(x=birds_dispersal_distance,y=calc_shannon_diversity,color=habitat_patch_size)) + geom_point() + scale_color_viridis_c(guide = FALSE) + facet_wrap( ~habitat_patch_size ) + theme_bw()

mdl1 %>% ggplot(aes(x=birds_dispersal_distance,y=deltaPop,color=habitat_patch_size)) + geom_point() + scale_color_viridis_c(guide = FALSE) + facet_wrap( ~habitat_patch_size ) + theme_bw()

mdl1 %>% filter(birds_dispersal_distance == 1.1 || birds_dispersal_distance == 3) %>% mutate(birds_dispersal_distance=factor(birds_dispersal_distance)) %>% ggplot(aes(x=habitat_patch_size,y=calc_number_of_species,color=birds_dispersal_distance)) + geom_point() + scale_color_viridis_d() + theme_bw()


# Plot for BirthSelection communities 
#

mdl <- read_netlogo_simul("Simulations/BirthSelection_pf06_hpf3-59_dd1-3_lambda2.csv")
sloss_sim <- bind_rows(sloss_sim,mdl)

## with migration

mdl <- read_netlogo_simul("Simulations/MultipleContactNeutralMigrat_BirthSelection_pf06_hpf3-59_dd1-3_lambda2.csv")
sloss_sim <- bind_rows(sloss_sim,mdl)

# Add Migration0_at_deforestation=FALSE to previous simulations 
#
unique(sloss_sim$Migration0_at_deforestation)
sloss_sim <- sloss_sim %>% mutate( Migration0_at_deforestation = if_else(is.na(Migration0_at_deforestation), FALSE, Migration0_at_deforestation )) 


#
#
mdl1 <- mdl %>% group_by(birds_dispersal_distance, habitat_patch_size) %>% summarise(across(birds_at_deforestation:count_birds,mean)) %>% mutate(deltaPop = (count_birds - birds_at_deforestation )/ birds_at_deforestation  )

mdl1 %>% ggplot(aes(x=birds_dispersal_distance,y=calc_number_of_species,color=habitat_patch_size)) + geom_point() + scale_color_viridis_c(guide = FALSE) + facet_wrap( ~habitat_patch_size ) + theme_bw()

mdl1 %>% ggplot(aes(x=birds_dispersal_distance,y=calc_shannon_diversity,color=habitat_patch_size)) + geom_point() + scale_color_viridis_c(guide = FALSE) + facet_wrap( ~habitat_patch_size ) + theme_bw()

mdl1 %>% ggplot(aes(x=birds_dispersal_distance,y=deltaPop,color=habitat_patch_size)) + geom_point() + scale_color_viridis_c(guide = FALSE) + facet_wrap( ~habitat_patch_size ) + theme_bw()

mdl1 %>% filter(birds_dispersal_distance == 1.1 || birds_dispersal_distance == 3) %>%
  mutate(birds_dispersal_distance=factor(birds_dispersal_distance)) %>% ggplot(aes(x=habitat_patch_size,y=calc_number_of_species,color=birds_dispersal_distance)) + geom_point() + scale_color_viridis_d() + theme_bw()

```



## Not fragmented communities Lambda = 1.7 - 4


```{r SLOSS_notfrag_simulations, echo=FALSE,message=FALSE,warning=FALSE,fig.align='center',eval=FALSE}
require(tidyverse)

source("R/functions.r")

# Not fragmented communities = habitat_patch_size = 100
#
mdl <- read_netlogo_simul("Simulations/NoHiBi_pf00_hpf3_dd1-3_lambda1.7-4.csv") %>% mutate(habitat_patch_size=100)

# New Simulations 
#
mdl <- read_netlogo_simul("Simulations/NoHiBi_pf00_hpf3_dd1-3_lambda1.1-4.csv") %>% mutate(habitat_patch_size=100)

sloss_sim <- bind_rows(sloss_sim,mdl)

# Add Migration0_at_deforestation=FALSE to previous simulations 
#
unique(sloss_sim$Migration0_at_deforestation)
sloss_sim <- sloss_sim %>% mutate( Migration0_at_deforestation = if_else(is.na(Migration0_at_deforestation), FALSE, Migration0_at_deforestation )) 
unique(sloss_sim$habitat_patch_size)
#sloss_sim <- sloss_sim %>% mutate( habitat_patch_size = if_else(habitat_patch_size==0, 100, habitat_patch_size )) 

saveRDS(sloss_sim, "Simulations/sloss_sim.rds")

names(mdl)
#
# Plot for neutral communities 
# I filter birth_rate_birds 1.1 because these communities survive only by migration
#
mdl1 <- mdl %>% filter(birth_rate_birds!=1.1) %>% group_by(birds_dispersal_distance, birth_rate_birds,birds_behavior) %>% summarise(across(birds_at_deforestation:count_birds,mean)) %>% mutate(birth_rate_birds = factor(birth_rate_birds)  ) 

mdl1 %>% ggplot(aes(x=birds_dispersal_distance,y=calc_number_of_species,color=birth_rate_birds)) + geom_point() + geom_line() + scale_color_viridis_d(name="lambda") + facet_wrap( ~birds_behavior )  + theme_bw() + ylab("Number of species") + xlab("Dispersal Distance") 
ggsave("Figures/Species_NoFrag_Dispersal_Lambda.png",width=8,height=6,units="in",dpi=600)


mdl1 %>% ggplot(aes(x=birds_dispersal_distance,y=calc_shannon_diversity,color=birth_rate_birds)) + geom_point() + scale_color_viridis_d() + facet_wrap( ~birds_behavior ) + theme_bw()

mdl1 %>% ggplot(aes(x=birds_dispersal_distance,y=count_birds,color=birth_rate_birds)) + geom_point() + geom_line() + scale_color_viridis_d(name="lambda") + facet_wrap( ~birds_behavior )  + theme_bw() + ylab("Number of indiv.") + xlab("Dispersal Distance") 
ggsave("Figures/Indiv_NoFrag_Dispersal_Lambda.png",width=8,height=6,units="in",dpi=600)

mdl1 %>% filter(birds_dispersal_distance == 1.1 || birds_dispersal_distance == 3) %>%  mutate(birds_dispersal_distance=factor(birds_dispersal_distance)) %>% ggplot(aes(x=birth_rate_birds,y=calc_number_of_species,color=birds_dispersal_distance)) + geom_point() + scale_color_viridis_d() + theme_bw()+ facet_wrap( ~birds_behavior )

```

## Add more simulations lambda = 2 with Migration 

```{r SLOSS_combined_plots, echo=FALSE,message=FALSE,warning=FALSE,fig.align='center',eval=FALSE}

mdl <- read_netlogo_simul("Simulations/NoHiBi_pf06_hpf3-61_dd1-3_lambda2_Migrat.csv") 

sloss_sim <- bind_rows(sloss_sim,mdl)

mdl <- read_netlogo_simul("Simulations/NoHiBi_pf06_hpf3-61_dd1-3_lambda2_NoMigrat.csv") 
sloss_sim <- bind_rows(sloss_sim,mdl)

mdl <- read_netlogo_simul("Simulations/NoHiBi_pf06_hpf3-61_dd1-3_lambda4_Migrat.csv") 
sloss_sim <- bind_rows(sloss_sim,mdl)

save.image()

#
# 200 x 200 - Started simulation 10:47
#
mdl <- read_netlogo_simul("Simulations/NoHiBi_200_pf06_hpf3-61_dd1-3_lambda2_NoMigrat.csv")
sloss_sim <- bind_rows(sloss_sim,mdl)
sloss_sim <- sloss_sim %>% mutate( world_width=if_else(is.na(world_width),100,world_width))
sloss_sim <- sloss_sim %>% mutate( world_width=if_else(world_width==99,100,world_width))

saveRDS(sloss_sim, "Simulations/sloss_sim.rds")

```


## Plots of combined behaviors and patch 100

```{r SLOSS_combined_plots1, echo=FALSE,message=FALSE,warning=FALSE,fig.align='center',eval=FALSE}
require(tidyverse)

source("R/functions.r")


#mdl1 <- sloss_sim %>% filter(Migration0_at_deforestation | (birth_rate_birds==2 & habitat_patch_size==100)) %>%  
sloss_sim %>% distinct(Migration0_at_deforestation, world_width)

#
# Count number of simulations
#
mdl1 <- sloss_sim %>% filter(Migration0_at_deforestation, world_width==100 ) %>%  
  count(habitat_patch_size,birds_dispersal_distance, birth_rate_birds,birds_behavior) 

mdl1 <- sloss_sim %>% filter(Migration0_at_deforestation, world_width==100 ) %>%  
  group_by(habitat_patch_size,birds_dispersal_distance, birth_rate_birds,birds_behavior) %>%
  summarise(across(birds_at_deforestation:count_birds,mean)) %>% mutate(birth_rate_birds = factor(birth_rate_birds)  )

#mdl1 %>% filter(birds_dispersal_distance == 1.1 || birds_dispersal_distance == 3 || birds_dispersal_distance == 1.5) %>%  
mdl1 %>% mutate(birds_dispersal_distance=factor(birds_dispersal_distance)) %>% ggplot(aes(x=habitat_patch_size,y=calc_number_of_species,color=birds_dispersal_distance)) + geom_point() + geom_line() + scale_color_viridis_d(name="Dispersal") + theme_bw()+ facet_wrap( ~birds_behavior ) + ylab("Number of species") + xlab("Patch Size") + ggtitle("Lambda=2 Degraded 60% NoMigration")

ggsave("Figures/Species_PatchSize_Dispersal_NoMigration.png",width=8,height=6,units="in",dpi=600)


mdl1 %>% mutate(birds_dispersal_distance=factor(birds_dispersal_distance)) %>% ggplot(aes(x=habitat_patch_size,y=calc_shannon_diversity,color=birds_dispersal_distance)) + geom_point() + geom_line() + scale_color_viridis_d(name="Dispersal") + theme_bw()+ facet_wrap( ~birds_behavior ) + ylab("Shannon diversity") + xlab("Patch Size") + ggtitle("Lambda=2 Degraded 60% NoMigration")
ggsave("Figures/Shannon_PatchSize_Dispersal_NoMigration.png",width=8,height=6,units="in",dpi=600)
  
#
# With migration all the time
#

mdl1 <- sloss_sim %>% filter(!Migration0_at_deforestation ) %>%  
  count(habitat_patch_size,birds_dispersal_distance, birth_rate_birds,birds_behavior)

#
# Plot without SD
#
mdl1 <- sloss_sim %>% filter(!Migration0_at_deforestation & habitat_patch_size!=100 & birth_rate_birds == 2, world_width==100 ) %>%  
  group_by(habitat_patch_size,birds_dispersal_distance, birth_rate_birds,birds_behavior) %>%
  summarise(across(birds_at_deforestation:count_birds,mean)) %>% mutate(birth_rate_birds = factor(birth_rate_birds)  )

mdl1 %>% mutate(birds_dispersal_distance=factor(birds_dispersal_distance)) %>% ggplot(aes(x=habitat_patch_size,y=calc_number_of_species,color=birds_dispersal_distance)) + geom_point() + geom_line() + scale_color_viridis_d(name="Dispersal") + theme_bw()+ facet_wrap( ~birds_behavior ) + ylab("Number of species") + xlab("Patch Size") + ggtitle("Lambda=2 Degraded 60% Migration")

ggsave("Figures/Species_PatchSize_Dispersal_Migration.png",width=8,height=6,units="in",dpi=600)



mdl1 %>% mutate(birds_dispersal_distance=factor(birds_dispersal_distance)) %>% ggplot(aes(x=habitat_patch_size,y=calc_shannon_diversity,color=birds_dispersal_distance)) + geom_point() + geom_line() + scale_color_viridis_d(name="Dispersal") + theme_bw()+ facet_wrap( ~birds_behavior ) + ylab("Shannon diversity") + xlab("Patch Size") + ggtitle("Lambda=2 Degraded 60% Migration")
ggsave("Figures/Shannon_PatchSize_Dispersal_Migration.png",width=8,height=6,units="in",dpi=600)


#
# From Lamda 2 to lambda 4 Neutral
#

mdl1 <- sloss_sim %>% filter(!Migration0_at_deforestation & habitat_patch_size!=100 & birds_behavior == "NoSelection" ) %>%  
  group_by(habitat_patch_size,birds_dispersal_distance, birth_rate_birds) %>%
  summarise(across(birds_at_deforestation:count_birds,mean)) %>% mutate(birth_rate_birds = factor(birth_rate_birds)  )

mdl1 %>% mutate(birds_dispersal_distance=factor(birds_dispersal_distance)) %>% ggplot(aes(x=habitat_patch_size,y=calc_number_of_species,color=birds_dispersal_distance)) + geom_point() + geom_line() + scale_color_viridis_d(name="Dispersal") + theme_bw()+ facet_wrap( ~birth_rate_birds ) + ylab("Number of species") + xlab("Patch Size") + ggtitle("Neutral - Degraded 60% - Migration 0.001")
ggsave("Figures/Species_lambda2-4_PatchSize_Dispersal_NoSelection.png",width=8,height=6,units="in",dpi=600)

#
# From Lamda 2 to lambda 4 Hierarchical
#


mdl1 <- sloss_sim %>% filter(!Migration0_at_deforestation & habitat_patch_size!=100 & birds_behavior == "Hierarchical" ) %>%  
  group_by(habitat_patch_size,birds_dispersal_distance, birth_rate_birds) %>%
  summarise(across(birds_at_deforestation:count_birds,mean)) %>% mutate(birth_rate_birds = factor(birth_rate_birds)  )

mdl1 %>% mutate(birds_dispersal_distance=factor(birds_dispersal_distance)) %>% ggplot(aes(x=habitat_patch_size,y=calc_number_of_species,color=birds_dispersal_distance)) + geom_point() + geom_line() + scale_color_viridis_d(name="Dispersal") + theme_bw()+ facet_wrap( ~birth_rate_birds ) + ylab("Number of species") + xlab("Patch Size") + ggtitle("Hierarchical - Degraded 60% - Migration 0.001")
ggsave("Figures/Species_lambda2-4_PatchSize_Dispersal_Hierarchical.png",width=8,height=6,units="in",dpi=600)


```



